I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-04-24 lipics-master/Paper_noProof.tex
format (anonymous...)

\author{Yuke Liao}{CNRS@CREATE, Singapore}{yuke.liao@cnrsatcreate.sg}{}{}

\author{Blaise Genest}{CNRS, France \and CNRS@CREATE, Singapore \and https://perso.crans.org/genest/}{blaise.genest@cnrsatcreate.sg}{}{}

\author{Kuldeep Meel}{University of Toronto, Canada \and https://www.cs.toronto.edu/~meel/}{ meel@cs.toronto.edu}{}{}

\author{Shaan Aryaman}{NYU Courant Institute of Mathematical Sciences, United States}{aryaman.shaan@gmail.com}{}{}

%\author{John Q. Public}{Dummy University Computing Laboratory, [optional: Address], Country \and My second affiliation, Country \and \url{http://www.myhomepage.edu} }{johnqpublic@dummyuni.org}{https://orcid.org/0000-0002-1825-0097}{(Optional) author-specific funding acknowledgements}

>>>>

%\author{Yuke Liao}{CNRS@CREATE, Singapore}{yuke.liao@cnrsatcreate.sg}{}{}

%\author{Blaise Genest}{IPAL Lab, CNRS and CNRS@CREATE, France and Singapore}{blaise.genest@cnrsatcreate.sg}{}{}

%\author{Kuldeep Meel}{University of Toronto, Canada}{ meel@cs.toronto.edu}{}{}

%\author{Shaan Aryaman}{NYU Courant Institute of Mathematical Sciences, United States}{aryaman.shaan@gmail.com}{}{}

%\author{John Q. Public}{Dummy University Computing Laboratory, [optional: Address], Country \and My second affiliation, Country \and \url{http://www.myhomepage.edu} }{johnqpublic@dummyuni.org}{https://orcid.org/0000-0002-1825-0097}{(Optional) author-specific funding acknowledgements}
%\authorrunning{Y. Liao, B. Genest, K. Meel and S. Aryaman} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'

\keywords{Dummy keyword} %TODO mandatory; please add comma-separated list of keywords

%\Copyright{Liao Yuke, Blaise Genest, Kuldeep Meel and Shaan Aryaman} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

\ccsdesc[100]{} %TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
